### 2018-05-11 msc_diploma_cubesat_galgoczi.tex
update

\vspace{1 cm}
\begin{large}\textbf{Detailed feasibility study of a gamma ray detector system for nanosatellites using GEANT4 simulations}\end{large}\\
\vspace{1 cm}
%\begin{larger}\textbf{BSc szakdolgozat}\\ \end{larger}
%\vspace{0.5 cm}
\textit{\textbf{Galgóczi Gábor$^{*}$, Fizikus MSc szak, 2. évfolyam}}\\
Eötvös Loránd Tudományegyetem, Természettudományi Kar\\
WIGNER Fizikai Kutatóközpont - MTA\\
\vspace{1.5cm}

@@

Most relevant parameters:
\begin{itemize}
\item absoprtion length of the scintillator material
\item scintillation yield
\end{itemize}

@@

>>>>

\vspace{1 cm}
\begin{large}\textbf{Detailed feasibility study of a gamma ray detector system for nanosatellites using GEANT4 simulations}\end{large}\\
\vspace{1 cm}
%\begin{larger}\textbf{BSc szakdolgozat}\\ \end{larger}
%\vspace{0.5 cm}
\textit{\textbf{Galgóczi Gábor$^{*}$, Fizikus MSc szak, 3. évfolyam}}\\
Eötvös Loránd Tudományegyetem, Természettudományi Kar\\
WIGNER Fizikai Kutatóközpont - MTA\\
\vspace{1.5cm}

@@

@@

The $\gamma$ source that was used to test the experimental setup was choosen to be an $^{241}Am$. The reason for this is that the peak of energy spectrum of the $\gamma$ photons from GRBs is at 50 keV which is very close to the peak of the $^{241}Am$ that is 59.5 keV. The activity of the source at the time of the experiment was 471 kBq. The source was collimated to a beam that hit the surface of the scintillator on a circle with a radius of 10 mm. The distance of the source from the scintillator was 13.5 mm. Therefore the number of $\gamma$s that hit the scintillator, the Al and Pb sheets above it was:
$$471 kBq \cdot \frac{s}{s}$$

Most relevant parameters:
\begin{itemize}
\item absoprtion length of the scintillator material
\item reflection of the ESR (Enchanced Specular Reflector) tape the is wrapped around the scintillator 
\item scintillation yield
\end{itemize}
